### 2019-12-16 tex/ms.tex
fix weird characters...
include zeropoint results table

>>>>

\begin{center}
\begin{table}[ht]
\begin{tabular}{c | c | c | c | c}
camera & amp & ZP (total raw ADU/s) & ZP (total e-/s) & assumed gain (e-/ADU, acceptance report) \\ \hline
GUIDE0 & E & 25.714 & 27.079 & 3.516 \\
GUIDE0 & F & 25.689 & 27.063 & 3.545 \\
GUIDE0 & G & 25.654 & 27.067 & 3.673 \\
GUIDE0 & H & 25.695 & 27.078 & 3.574 \\
GUIDE2 & E & 25.633 & 27.045 & 3.668 \\
GUIDE2 & F & 25.612 & 27.035 & 3.708 \\
GUIDE2 & G & 25.654 & 27.067 & 3.673 \\
GUIDE2 & H & 25.627 & 27.057 & 3.733 \\
GUIDE3 & E & 25.652 & 27.063 & 3.669 \\
GUIDE3 & F & 25.679 & 27.058 & 3.560 \\
GUIDE3 & G & 25.615 & 27.061 & 3.785 \\
GUIDE3 & H & 25.623 & 27.052 & 3.729 \\
GUIDE5 & E & 25.626 & 27.052 & 3.718 \\
GUIDE5 & F & 25.630 & 27.062 & 3.741 \\
GUIDE5 & G & 25.636 & 27.066 & 3.733 \\
GUIDE5 & H & 25.621 & 27.066 & 3.787 \\
GUIDE7 & E & 25.569 & 27.036 & 3.863 \\
GUIDE7 & F & 25.664 & 27.063 & 3.629 \\
GUIDE7 & G & 25.494 & 27.011 & 4.043 \\
GUIDE7 & H & 25.512 & 27.008 & 3.967 \\
GUIDE8 & E & 25.615 & 27.047 & 3.740 \\
GUIDE8 & F & 25.601 & 27.048 & 3.793 \\
GUIDE8 & G & 25.699 & 27.090 & 3.601 \\
GUIDE8 & H & 25.652 & 27.072 & 3.698 \\
\end{tabular}
\caption{zeropoint results}
\label{tab:zps}
\end{table}
\end{center}
